---
title: "Final Exam"
author: "Patricia Rodrigues"
date: 12/12/2020
output: pdf_document
---





### What does it mean to do reproducible research? Why is reproducibility important to the process of science? (5 pts)

Reproducibility is the ability to obtain the same results using the same data. Reproducible research allows other researchers to reproduce a study by providing data, code, methods, analysis, operating system, etc., essentially everything needed to replicate a study. It's an important process because it allows us to not only validate the credibility and results of a study, but also to build on the knowledge from that study without having to start from scratch. Science is continually building on itself, so having open and transparent science is crucial to the integrity of the research.



###  Using the data on red wine quality, develop a predictive model of red wine quality. Format the model in a way that it works well with the `predict` function in `R`. You will be assessed on the model structure mostly, but 5 of the 10 points will be on if the model can outperform a naive baseline (10 pts)



```{r}
setwd("/biol4800-final-exam")
dat <- read.csv('redWineTrain.csv', header = TRUE, row.names = 1)
var.sel <- lm(quality ~ density + residual.sugar + citric.acid + alcohol + total.sulfur.dioxide + volatile.acidity + free.sulfur.dioxide + sulphates + pH + chlorides + fixed.acidity, data = dat)
mod1 <- lm(quality ~ alcohol + volatile.acidity + sulphates + chlorides, data = dat)
mod2 <- lm(quality ~ alcohol + volatile.acidity + sulphates, data = dat)
mod3 <- lm(quality ~ alcohol + volatile.acidity, data = dat)
mod4 <- lm(quality ~ alcohol, data = dat)

## Created 4 models based on most significant variables, final model had highest adjusted r-squared and lowest p-value with fewest variables
final.mod <- mod2
## look at model summary
summary(mod2)
## look at QQ plots
 layout(matrix(1:4, ncol=2)) 
 par(mar=c(4,4,0.5,0.5)) 
 plot(final.mod)
 ## residuals roughly centered around zero
 hist(final.mod$residuals)
## see how well model predicts data
qual <-  seq(4,10, by = 0.25)
alc <- seq(8, 14, by = 0.25) 
vol <- seq(0.2, 1.425, by = 0.025)
sulf <- seq(0.06, 3, by = 0.06)

pred <- data.frame(quality = qual, alcohol = alc, volatile.acidity = vol, sulphates = sulf)
preds <- as.data.frame(predict(final.mod, new = pred, interval = "confidence"))

```



### Pull data from an API of your choice (not Open Library), manipulate it in any way you choose, and create the most interesting and clear figure you can. (15 pts)

(See https://rapidapi.com/blog/most-popular-api/ for a list of APIs)

```{r}
library("httr")
library("jsonlite")

anime <- httr::GET("https://anilistmikilior1v1.p.rapidapi.com/getAnimeList")
animeInfo <- jsonlite::fromJSON(content(anime, "text"), simplifyVector = FALSE)

```



### Use the R package `rgbif` to obtain occurrence data for a species of your choosing. Calculate the spatial distance between all occurrence points in a pair-wise fashion. (10 pts)



```{r}
install.packages(c("rgbif", "geosphere", "dplyr"))
library(rgbif)
library(geosphere)
library(dplyr)

cardinal <- rgbif::occ_search(scientificName = 'Cardinalis cardinalis', limit = 10, return = 'data')[[3]]


# calculate distance
cardLocs <- select(cardinal, decimalLatitude, decimalLongitude)
cardDists <- array()
for(i in 1:nrow(cardLocs)) {
  dist[i] <- distm(c(cardLocs$decimalLongitude[i], cardLocs$decimalLatitude[i]), c(cardLocs$decimalLongitude[i + 1], cardLocs$decimalLatitude[i + 1]), fun = distHaversine)
}
cardDists

```




### Write an R function that removes each value of a vector, calculates the mean of the modified vector, and then reports the overall mean and standard deviation of those vector means. (5 pts)


```{r}

vec <- c(1:10)
vec2 <- c(1, 2, 3, NA, 5, 10)
vec3 <- c(1, 2, 3, "poop", 5, 6)
## arguments, vector and which element of the vector to be removed
vecFunc <- function(vector, remove) {
  if(!is.numeric(vector)) {
    warning("vector must be numeric")
  }
  temp <- vec[-remove]
  out <- c(mean(temp, na.rm = TRUE), sd(temp, na.rm = TRUE))
  
  return(out)
}
  
```






### Choose a software license that is one you would feel comfortable using and defend it's use over other licenses (5 pts)












### Which of the following softwares are you likely to use in the future? (0 pts)

+ R
+ git
+ R markdown
+ LaTeX
+ SQL
+ parallel computing packages
+ Docker
+ the tidyverse
+ a Linux OS
+ bash shell







### What did you enjoy most about the course?




### What could be improved for future iterations (especially as it will be geared more exclusively towards undergraduates in the future)?



